---
title: <center> <h1>  REGION WISE DETAILS </h1> </center>
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "Omer Sharif"
date: "7/27/2021"
output: 
 rmarkdown::html_document:
  theme: journal
  toc: false
  toc_float: false
  highlight: tango
  number_sections: false
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(plotly)
library(ggthemes)
library(dplyr)
library(viridis)
library(DT)
library(readxl)

# Induct In Ethanol Excel Sheet
Main <- read_excel("C:/Users/omer.sharif/Desktop/Office Computer/Capstone/R Codes/Ethanol Dashboard/Jun 2021/Main.xlsm")


```


# INTERACTIVE REPORT

* Hover of the mouse _highlights "Date","Price", and "Region"_. 
* `Colours` represent different _Regions_.

```{r products,echo=FALSE,fig.align='center',fig.width=10,fig.height=5}

REGION <- as.factor(Main$REGION)
p <- ggplot(data=Main,aes(x= DATE ,y=`M.Ton Price`,fill=REGION))
p <- p + geom_point(alpha=0.3) + geom_jitter(alpha=0.3) +
  theme(legend.position = "top",plot.title=element_text(hjust=0.5)) + labs(title="ETHANOL PRICES PER METRIC TON - YEAR 2017 TO 2021",x="",y="")
p <- p + facet_grid(.~Product) + scale_fill_viridis_d() + guides(fill="none") 
p <- ggplotly(p) 
hide_legend(p) %>% config(displaylogo = FALSE) %>%  config(displayModeBar = FALSE) 
```

### DATA SUMMARY BY YEAR

* Table is a summary of prices based on _Year_ basis.
* `Maximum` and `Minimum` prices are grouped for one _"product"_ within a _"region"_ for that **year** for multiple _"Obs"_ observations. For example, in year 2021 for product _ENA 96%_ in Asia there are `522` observations. There is no other case of _ENA 96%_ in year 2021 for Asia.
* Each record in the table below is unique in such a way


```{r,message= FALSE}
Product_count <- Main %>% group_by(Year,Product,REGION) %>%
summarise(Obs=n(),`Maximum Price`= round(max(`M.Ton Price`),2),`Minimum Price`=round(min(`M.Ton Price`),2))
Product_count <- Product_count %>% arrange(desc(Year),desc(Product))

datatable(Product_count)

```


